A new breeding crossover approach for evolutionary algorithms

### 2023-09-21 paper.tex
Functions F1 to F10 update

    We describe how to interpret the results presented in our Box and Whisker charts for each mathematical function. We display the ten and thirty-dimension charts on the left and right sides. We can find the results accumulated in 51 runs, in green color the One Point crossover, and in blue color the Continuous Range crossover. The closer the error results get to the zero value, the better.

>>>>

    We describe how to interpret the results presented in our Box and Whisker charts for each mathematical function. We display the ten and thirty-dimension charts on the left and right sides. We can find the results accumulated in 51 runs, in green color the One Point crossover, and in blue color the Continuous Range crossover. The closer the error results get to the zero value, the better. Below, we describe Figure~\ref{fig.experiment_F1-F5}, which includes Functions 1 to 5 (F1 to F5).

    \begin{itemize}
        \item In function F1 for the ten-dimensional category, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test. We needed to find more evidence for the thirty dimensions category to determine whether any crossover alternative would be better.
        \item At function F2 for the category of 10 dimensions, again, the CRx strategy outperformed the alternative approach OPx in the statistical test. More evidence was required for the thirty dimensions category to declare any of them as the best.
        \item At function F3 for both categories, 10 and 30 dimensions, the statistical test found better results for our proposed CRx strategy than the alternative OPx.
        \item At function F4, only for the 10-dimensional category, the CRx strategy proved to be better through the statistical test, while for the 30-dimensional variety, it could not identify any of them as the best.
        \item At function F5, only for the 10-dimensional category, the proposed strategy CRx passed the statistical test to its alternative OPx, while for the 30-dimensional type, they obtained similar results.
    \end{itemize}

    We describe the results shown in Figure~\ref{fig.experiment_F6-F10}, including functions F6 through F10.

    \begin{itemize}
        \item In function F6, for the category of 10 dimensions, there needed to be more evidence to determine that any of the proposals were best. For the variety of 30, the OPx alternative surpassed our CRx proposal in the statistical test for the first occasion.
        \item At function F7, for the category of 10 dimensions, once again, the CRx strategy outperforms its alternative through the statistical test. For the 30-dimension type, we found not enough evidence to declare any of them as the best proposal.
        \item At function F8, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
        \item At function F9, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
        \item At function F10, the opposite of the previous function occurred, where for both dimensions, 10 and 30, the classic OPx strategy obtained better results than our CRx proposal by passing the statistical test in both cases.
    \end{itemize}
